---
title: "HW3"
author: "Vanesa Avoyan"
date: "`r Sys.Date()`"
output: pdf_document
---

Neccessary libraries
```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(stringr)
```

Loading the dataset
```{r}
mobiles_dataset <- read.csv("mobiles_dataset.csv")
```

Part 1.
```{r}
mobiles_dataset$Launched.Price.Pakistan.PKR <-
  mobiles_dataset$Launched.Price.Pakistan.PKR * 0.0036
mobiles_dataset$Launched.Price.India.INR <-
  mobiles_dataset$Launched.Price.India.INR * 0.011
mobiles_dataset$Launched.Price.China.CNY <-
  mobiles_dataset$Launched.Price.China.CNY * 0.14
mobiles_dataset$Launched.Price.Dubai.AED <-
  mobiles_dataset$Launched.Price.Dubai.AED * 0.27
```


```{r}
Mobile1 <- mobiles_dataset %>%
  pivot_longer(cols = starts_with("Launched.Price."), 
               names_to = "Country", 
               values_to = "Price") %>%
  mutate(Country = gsub("Launched.Price_", "", Country)) %>%
  mutate(Country = str_extract(Country, "(China|Dubai|India|Pakistan|USA)\\.[A-Z]{3}"))
```

1)
```{r}
Mobile1.1 <- Mobile1 %>%
  group_by(Country, Battery.Capacity.mAh) %>%
  summarise(Std_of_Price = sd(Price, na.rm = TRUE), .groups = "drop") %>%
  filter(!is.na(Std_of_Price))
```


```{r}
ggplot(data = Mobile1.1, aes(x = Battery.Capacity.mAh,
                             y = Std_of_Price,
                             colour = Country)) +
  geom_point() +
  facet_grid(~Country) +
  labs(title = "Battery Capacity VS Price",
       x = "Battery Capacity",
       y = "Price") +
  theme_minimal()
```

The Capacity influence is nearly the same.

2)
```{r}
ggplot(data = Mobile1, aes(x = RAM,
                           y = Price,
                           fill = Country)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "RAM VS Price",
       x = "RAM",
       y = "Price") +
  theme_minimal()
```

Yes. The RAM with 12 GB and 8 GB are the most expensive ones. Through the Pakistan prices are significantly lower.

3)
```{r}
ggplot(data = Mobile1, aes(x = Company.Name,
                           y = Price,
                           fill = Country)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Brand VS Price",
       x = "Brand",
       y = "USA price") +
  theme_minimal()
```

Not only Apple has big variance but also other brands. For the Apple India has the highest markup.There are Poco, Nokia, Lenovo that have more stable pricing policy.

4)
```{r}
Mobile1$Affordability <- c("1")
```

```{r}
for (i in 1:nrow(Mobile1)) {
  if (Mobile1$Price[i] > 700) {
    Mobile1$Affordability[i] = "Premium"
  } else if (Mobile1$Price[i] < 300) {
    Mobile1$Affordability[i] = "Budget"
  } else (Mobile1$Affordability[i] = "Mid-range")
}
```

```{r}
ggplot(data = Mobile1, aes(x = Company.Name,
                           fill = Affordability)) +
  geom_bar(position = "fill") +  
  labs(title = "Affordability Segment Distribution",
       x = "Affordability Segment",
       y = "Proportion") +
  theme_minimal()
```

Here we can see that Nokia is only Budget priced phones. But brands like Apple, Sony and Huawei are Premium oriented.

5)
```{r}
Mobile1.2 <- Mobile1 %>%
  group_by(Country, Affordability, Company.Name) %>%
  summarise(Avg_Price = mean(Price), .groups = "drop")
```

```{r}
ggplot(data = Mobile1.2, aes(x = Company.Name,
                             fill = Affordability)) +
  geom_bar(position = "fill") +
  facet_wrap(~Country) +
  labs(title = "Affordability Segment Distribution by Country",
       x = "Affordability Segment",
       y = "Proportion") +
  theme_minimal()
```

Pakistan offers the most affordable prices.

Part 2.
1)
```{r}
ggplot(data = Mobile1.2, aes(x = Country,
                             y = Avg_Price, 
                             fill = Country)) +
  geom_bar(stat = "identity") +
  labs(title = "Bar chart of Countries average prices",
       x = "Country",
       y = "Price") +
  theme_minimal()
```

2)
```{r}
Mobile2.1 <- Mobile1 %>%
  group_by(Company.Name) %>%
  summarise(Market_Share = n())
```


```{r}
ggplot(data = Mobile2.1, aes(x = "",
                             y = Market_Share,
                             fill = Company.Name)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = "Market Share by Company",
       x = "",
       y = "Market Share") +
  theme_minimal()
```


Part 3.
1)
```{r}
Mobile3.1 <- Mobile1 %>%
  filter(Country == "USA.USD")
```

```{r}
ggplot(data = Mobile3.1, aes(x = Company.Name,
                             y = Price,
                             fill = Company.Name)) +
  geom_boxplot() +
  geom_point() +
  labs(title = "Price distribution by Company in USA",
       subtitle = "A boxplot showing how the price variesby company, with individual data points overlaid",
       x = "Company",
       y = "Price in USD",
       fill = "Company Name") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45),
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "italic"))
```

2)
```{r}
ggplot(data = Mobile3.1, aes(x = Battery.Capacity.mAh,
                             y = Price,
                             colour = Company.Name,
                             size = Screen.Size.inches)) +
  geom_point() +
  labs(title = "Battery Capacity VS Price in USA",
       subtitle = "The relationship between capacity, price, and screen size across different smartphone brands",
       x = "Battery Capacity",
       y = "Price",
       color = "Brand") +
  theme_minimal() +
  theme(
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "italic")) +
  guides(size = "none")
```

3)

```{r}
Top_Brands <- c("Apple", "Honor", "Oppo", "Samsung", "Vivo")
Mobile3.2 <- Mobile1 %>%
  filter(Company.Name %in% Top_Brands)
```

```{r}
ggplot(data = Mobile3.2, aes(x = Battery.Capacity.mAh,
                             y = Price,
                             colour = Screen.Size.inches,
                             size = Battery.Capacity.mAh,
                             shape = Company.Name)) +
  geom_point(alpha = 0.7) +
  labs(title = "Battery Capacity VS Price for Top 5 Brands",
       subtitle = "Different Shapes for Each Brand, Color by Screen Size, (USA)",
       x = "Battery Capacity",
       y = "Price",
       shape = "Brand") +
  theme_minimal() +
  theme(
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "italic")) +
  guides(colour = "none", size = "none") +
  scale_shape_manual(values = c(16, 17, 18, 15, 19))
```

